---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The Extended Axiomatic Design (EAD)

<!-- badges: start -->

<!-- badges: end -->

The numerical EAD framework generates firm environments according to the Extended Axiomatic Design (EAD) introduced by Mertens (2020), Meßerschmidt et al. (2020) and Schmidt et al. (2021). The simulation model is explained in Meßerschmidt (forthcoming). The framework adapts some function from the cost system design framework by Anand et al. (2019). The original code in C# is available under <https://github.com/vanand74/CostSystemSim>.

## Installation

You can install the development version of EAD via any github install function. For example:

```{r, eval=FALSE, include=TRUE}
library(devtools)
install_github("olemesser/EAD",build_vignettes = TRUE)
```

## Create the EAD

First, load all relevant libraries:

```{r loading_init, eval=T, include=F}
#### Load Libraries ####
library(EAD)
library(dplyr)
library(tidyr)
library(parallel)
library(doSNOW)
library(foreach)
library(R.utils)
library(ids)
```

```{r loading, eval=F, include=TRUE}
#### Load Libraries ####
library(EAD)
library(dplyr)
library(tidyr)
library(parallel)
library(doSNOW)
library(foreach)
library(R.utils)
library(ids)
```

Second, define global parameter such as the output path, seed and a timeout. Important note: the `time_limit` variable must be defined as a global variable via double arrows as shown below. In this example, the EAD generation process is interrupted after 20 seconds. The individual time limit may vary from hardware configuration and input values defined by the design of experiments

```{r parameter, eval=T, include=TRUE}
set.seed(1234) # set random seed to reproduce the results
```

Third, define a design of experiment (DoE). For each

```{r doe, eval=T, include=TRUE}
 DOE<-expand_grid(N_FR = 8, # number of functional requirements
                   N_DD = 14, # number of physical domain elements
                   N_PrD = 30, # number of process domain elements
                   N_RD = 60, # number of resource domain elements
                   DNS = list(c(0.05,0.5)), # density of the functional product mix
                   method_FD = "DNS", # method to create the product mix
                   N_PROD = list(c(20,25)), # number of products
                   TOTAL_DEMAND = list(c(100,10000)), # total demand
                   Q_VAR = list(c(0,1.7)), # demand heterogeneity
                   DMM_PAR = expand_grid(FD_PD=list(c(0,0.1)),
                                PD_PrD=list(c(0,0.05)),
                                PrD_RD=list(c(0,0.05))), # desired system design complexity
                   uB_DMM = 10,
                   allowZero = T,
                   ut_DMM = F, # if the upper triangle DMMs should be generated too (DMM_FD_PrD,DMM_FD_RD,DMM_PD_RD)
                   DSM_param=expand_grid(PD=list(c(0,0.1,0,1)),
                                       PrD=list(c(0,0,0,1)),
                                       RD=list(c(0,0,0,1))), # first two entries refer to the density of the DSMs and the second pair to the cv if the DSM_method='modular' is used.
                   DSM_method='modular',
                   ub_DSM = 1,
                   TC = 10^6, # total costs
                   r_in = list(c(0,0.9)),
                   r_fix = list(c(0,1)), # proportion of fixed costs on total costs
                   RC_sdlog = list(c(0.1,2)), # skewness of resource costs
                   N_RUN = 1:4 # number of runs
                    )
```

Now you are ready to run the model. In this example, the EAD is created only for the first four rows of `DOE`. The code is optimized to multi-core processing. Where `NUMB_CORES` defines the number of cores used.

```{r run_silent, eval=T, include=F}
## run EAD generation procedure
  EAD<-crt_EAD_MC(DOE[1:4,],
                  NUMB_CORES = 4,
                  logfile= "" )
```

```{r run, eval=F, include=TRUE}
## run EAD generation procedure
  EAD<-crt_EAD_MC(DOE[1:4,],
                  NUMB_CORES=4,
                  logfile="")
```

Finally, write the created EAD environments to a file to conduct further experiments

```{r write, eval=FALSE, include=TRUE}
  ## write output to file
  save(EAD,file=paste0(Sys.Date(),"_EAD.RData"))
```

## Calculate (true) Benchmark Costs

The following chunk calculates the product benchmark costs for the given design.

```{r costs, eval=T, include=TRUE}
# variable indirect costs and the direct costs which are always variable are summed up
costs<- clc_PCB(RES_CONS_PAT = EAD[[1]][[1]]$P$RD,
                DMD = EAD[[1]][[1]]$DEMAND,
                RC_var_i = EAD[[1]][[1]]$RC$var_i,
                RC_var_d = EAD[[1]][[1]]$RC$var_d,
                RC_fix_i = EAD[[1]][[1]]$RC$fix_i,
                RC_fix_d = EAD[[1]][[1]]$RC$fix_d)

## the product costs multiplied by the demand equals the total costs
sum(costs$PC_B*EAD[[1]][[1]]$DEMAND)

```

To access the total product costs use the following arguments:

```{r totalcosts, eval=T, include=TRUE}
## total product costs
costs$PC_B
```

For the indirect benchmark costs use:

```{r indirectcosts, eval=T, include=TRUE}
## indirect benchmark product costs
costs$PC_B_indirect
```

If the product mix (available products) or the demand varies, the costs are calculated as:

```{r costs_varies, eval=TRUE, include=TRUE}
## lets assume we drop the first ten products 
DMD<-EAD[[1]][[1]]$DEMAND
DMD[1:10]<-0
costs_reduced<-clc_PCB(RES_CONS_PAT = EAD[[1]][[1]]$P$RD,
               DMD = DMD,
               RC_fix_i = EAD[[1]][[1]]$RC$fix_i,
               RC_fix_d = EAD[[1]][[1]]$RC$fix_d,
               RCU_indirect = costs$RCU_indirect,
               RCU_direct = costs$RCU_direct)

PC_B_reduced<-costs_reduced$PC_B

## compare the differences
summary<- data.frame(DMD_f = EAD[[1]][[1]]$DEMAND,
                   DMD_r = DMD,
                   PC_B_f = costs$PC_B,
                   PC_B_r = costs_reduced$PC_B,
                   PC_var_f = costs$PC_B_var_d + costs$PC_B_var_i,
                   PC_var_r = costs_reduced$PC_B_var_d + costs_reduced$PC_B_var_i,
                   PC_fix_f = costs$PC_B_fix_d + costs$PC_B_fix_i,
                   PC_fix_r = costs_reduced$PC_B_fix_d + costs_reduced$PC_B_fix_i)

summary
```

# Full Documentation

For the full documentation use the included vignettes as:

```{r,eval=FALSE, include=TRUE}
## list available vignettes
utils::vignette(package = "EAD")

## opens main documentation
utils::vignette("createEAD",package ="EAD")

## opens the setup for product costing system experiments
utils::vignette("pcs-experiment",package ="EAD")

## opens the setup forthe complexity cost experiment
utils::vignette("cc-experiment",package ="EAD")
```

This frameworks further comes with some example data sets reported in literature. To get on overview of available data sets call:

```{r include=TRUE, eval=FALSE}
data(package = "EAD")
```

# Acknowledgement

Special thanks to [Prof. Matthias Meyer](https://www.researchgate.net/profile/Matthias-Meyer-12 "Visit on Research Gate"), [Kai G. Mertens](https://www.researchgate.net/profile/Kai-G-Mertens "Visit on Research Gate") and [Mark Schmidt](https://www.researchgate.net/profile/Mark-Schmidt-19 "Visit on Research Gate") for detailed discussions during the development of this framework.

# References

Anand, V., Balakrishnan, R., & Labro, E. (2019). A Framework for Conducting Numerical Experiments on Cost System Design. *Journal of Management Accounting Research*, *31*(1), 41--61. <https://doi.org/10.2308/jmar-52057>

Mertens, K. G. (2020). *Measure and manage your product costs right -- development and use of an extended axiomatic design for cost modeling.* TUHH Universitätsbibliothek. <https://doi.org/10.15480/882.2888>

Meßerschmidt, O., Gumpinger, T., Meyer, M. & Mertens, K. G. Reviewing Complexity Costs -- What Practice Needs and What Research Contributes Proceedings of the Design Society: DESIGN Conference, 2020. Cambridge University Press, 647-656. <https://doi.org/10.1017/dsd.2020.152>

Meßerschmidt, O. (forthcoming). Variety and Costs - The Effects of Product Variety on Costs and Costing Systems.

Meyer, M., Meßerschmidt, O., & Mertens, K. G. (2019). *How much does variety-induced complexity actually cost? Linking axiomatic design with cost modelling*. In M. Schröder & K. Wegner (Eds.), *Logistik im Wandel der Zeit -- Von der Produktionssteuerung zu vernetzten Supply Chains* (pp. 813--827). Wiesbaden: Springer Fachmedien Wiesbaden. <https://doi.org/10.1007/978-3-658-25412-4_39>

Schmidt M, Mertens KG, Meyer M (2023) Cost hierarchies and the pattern of product cost cross-subsidization: Extending a computational model of costing system design. PLOS ONE 18(9): e0290370. <https://doi.org/10.1371/journal.pone.0290370>
