---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The Extended Axiomatic Design (EAD)

<!-- badges: start -->

<!-- badges: end -->

The numerical EAD framework generates firm environments according to the Extended Axiomatic Design (EAD) introduced by Mertens (2020). The simulation model is explained in Meßerschmidt (forthcoming). The framework adapts some function from the cost system design framework by Anand et al. (2019). The original code in C# is available under <https://github.com/vanand74/CostSystemSim>.

## Installation

You can install the development version of EAD via any github install function. For example:

```{r, eval=FALSE, include=TRUE}
library(devtools)
install_github("olemesser/EAD")
```

## Create the EAD

First, load all relevant libraries:

```{r loading, eval=FALSE, include=TRUE}
#### Load Libraries ####
library(EAD)
library(dplyr)
library(tidyr)
library(parallel)
library(doSNOW)
library(foreach)
library(R.utils)
library(ids)
```

Second, define global parameter such as the output path, seed and a timeout. Important note: the `time_limit` variable must be defined as a global variable via double arrows as shown below. In this example, the EAD generation process is interrupted after 20 seconds. The individual time limit may vary from hardware configuration and input values defined by the design of experiments

```{r parameter, eval=FALSE, include=TRUE}
set.seed(1234) # set random seed to reproduce the results
time_limit <<- 20 # global time limit in seconds
# setwd()
```

Third, define a design of experiment (DoE). For each

```{r doe, eval=FALSE, include=TRUE}
 DOE<-expand_grid(N_FR = 8, # number of functional requirements
                   N_DD = 14, # number of physical domain elements
                   N_PrD = 30, # number of process domain elements
                   N_RD = 60, # number of resource domain elements
                   PARAM_FD = seq(0.1,1,0.1), # percentage of products included
                   method_FD = "random",
                   TOTAL_DEMAND = 10000, # total demand
                   DMD_cv = list(c(0,3)), # demand skewness
                   DMM_PAR = list(c(0,0.05)), # desired design complexity
                   DMM_method="SDC", # method for generating the DMM
                   ut_DMM = F, # if the upper triangle DMMs should be generated
                   DSM_param=list(c(0,0.1)), # density of the DSMs
                   TC = 10^6, # total costs
                   ratio_fixedC = list(c(0.2,0.8)), # prop. of fixed costs on TC 
                   RC_cor = list(c(0,1)),# cor of resource costs
                   RC_cv = list(c(0,1)), # skewness of resource costs
                   N_RUN = 1:100 # number of runs
                    )
```

Now you are ready to run the model. In this example, the EAD is created only for the first four rows of `DOE`. The code is optimized to multi-core processing. Where `NUMB_CORES` defines the number of cores used.

```{r run, eval=FALSE, include=TRUE}
## run EAD generation procedure
  EAD<-crt_EAD_MC(DOE[1:4,],
                  NUMB_CORES=c(4),
                  logfile="")
```

Finally, write the created EAD environments to a file to conduct further experiments

```{r write, eval=FALSE, include=TRUE}
  ## write output to file
  save(EAD,file=paste0(Sys.Date(),"_EAD.RData"))
```

# References

Anand, V., Balakrishnan, R., & Labro, E. (2019). A Framework for Conducting Numerical Experiments on Cost System Design. *Journal of Management Accounting Research*, *31*(1), 41–61. <https://doi.org/10.2308/jmar-52057>

Mertens, K. G. (2020). *Measure and manage your product costs right – development and use of an extended axiomatic design for cost modeling.* TUHH Universitätsbibliothek. <https://doi.org/10.15480/882.2888>

Meyer, M., Meßerschmidt, O., & Mertens, K. G. (2019). *How much does variety-induced complexity actually cost? Linking axiomatic design with cost modelling*. In M. Schröder & K. Wegner (Eds.), *Logistik im Wandel der Zeit – Von der Produktionssteuerung zu vernetzten Supply Chains* (pp. 813–827). Wiesbaden: Springer Fachmedien Wiesbaden. <https://doi.org/10.1007/978-3-658-25412-4_39>

Meßerschmidt, O. (forthcoming). *Variety and Costs - The Effects of Product Variety on Costs and Costing Systems.*
